Learning constraints in tabular data

### 2016-05-12 Paper/ECAI/tabular.tex
comments

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/constraint_dependency.png}
  \caption{Dependency graph; an arrow from~$s_1$ to~$s_2$ indicates that $s_1$ is implied by $s_2$ because the \CSignature of~$s_2$ depends on $s_1$ to hold on a specific subset of $s_2$ its groups.
  }
  \label{fig:learning_order}
\end{figure}

@@

\paragraph{Example}
We show this construction of a CSP for the constraint template $\ecsumprod{G'}{H'}{I'}$ in Table~\ref{table:constraints}. It defines that $G'$ is a cell whose values is the result of the sum of products of rows in $H'$ and columns in $I'$.
%
There are three \textit{variables} $X, Y, Z$ corresponding to group $G'$, $H'$ and $I'$ respectively. The domains are $D(X) = D(Y) = D(Z) = \{1, \ldots, |{\cal G}|\}$. Finally, the constraints are:
\begin{align*}
&numeric(X) \land numeric(Y) \land numeric(Z) \\
&\pcols(X) = 1 \land \prows(X) = 1 \\
&\plength(Y) = \plength(Z) \land \plength(Y) \geq 2
\end{align*}
\tias{Sumproduct is a rather peculiar constraint for spreadsheets... perhaps switch to one with a dependency, e.g. look-up?}
\\\\

@@

\paragraph{Redundancy}
Mention 'largest overlapping subgroup' here?

@@

\subsection{Benchmark}
There are three main categories of spreadsheets in the benchmark: spreadsheets from an exercise session teaching Excel at an affiliated University, spreadsheets from tutorials online and publicly available spreadsheets such as crime statistics or financial reports that demonstrate more real world usage\footnote{\samuel{link to links.txt}}.
The case study is also included.

@@

\begin{table}
  \centering
  \begin{tabular}{lll}
    & \textbf{Total} & \textbf{Average per spreadsheet} \\
    \textbf{Constraints} & $93$ & $2.91$ \\
    \textbf{Accuracy} & $96.77\%$ & $94.27\%$ \\
    \textbf{Redundant} & $23.14\%~(28)$ & $8.33\%~(0.88)$ \\
    \textbf{Speed (s)} & ${\runtotal}s \pm {\runtotalstd}s$ & ${\runfile}s \pm {\runfilestd}s$
  \end{tabular}
  \caption{Overview evaluation on essential constraints of the collected Spreadsheet dataset}
\end{table}
\samuel{Expand summary}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/constraint_dependency.png}
  \caption{Dependency graph; an arrow from~$s_1$ to~$s_2$ indicates that $s_1$ is implied by $s_2$ because the \CSignature of~$s_2$ depends on $s_1$ to hold on a specific subset of $s_2$ its groups.
    The graph is extracted from the Signature column in Table \ref{table:constraints}.
  }
  \label{fig:learning_order}
\end{figure}

@@

\paragraph{Example}
We show this construction of a CSP for the constraint template $\ecsumprod{G'}{H'}{I'}$ in Table~\ref{table:constraints}. It defines that $G'$ is a cell whose values is the result of the sum of products of rows in $H'$ and columns in $I'$.
%
There are three \textit{variables} $X, Y, Z$ corresponding to group $G'$, $H'$ and $I'$ respectively. The domains are $D(X) = D(Y) = D(Z) = \{1, \ldots, |{\cal G}|\}$. Finally, the constraints are:
\begin{align*}
&numeric(X) \land numeric(Y) \land numeric(Z) \\
&\pcols(X) = 1 \land \prows(X) = 1 \\
&\plength(Y) = \plength(Z) \land \plength(Y) \geq 2
\end{align*}
\tias{Sumproduct is a rather peculiar constraint for spreadsheets... perhaps switch to one with a dependency, e.g. look-up?}
\sergey{ok, we need to see if look-up would fit here}
\\\\

@@

\paragraph{Redundancy}
\sergey{Samuel, probably it is better if you look here}
Mention 'largest overlapping subgroup' here?

@@

\subsection{Benchmark}
There are three main categories of spreadsheets in the benchmark: spreadsheets from an exercise session teaching Excel at an affiliated University, spreadsheets from tutorials online and publicly available spreadsheets such as crime statistics or financial reports that demonstrate more real world usage\footnote{(attached to to the submitted paperthe submitted paper)}.
The case study is also included.

@@

\begin{table}
  \centering
  \begin{tabular}{lll}
    & \textbf{Total} & \textbf{Average per spreadsheet} \\
    \textbf{Constraints} & $93$ & $2.91$ \\
    \textbf{Accuracy} & $96.77\%$ & $94.27\%$ \\
    \textbf{Redundant} & $23.14\%~(28)$ & $8.33\%~(0.88)$ \\
    \textbf{Speed (s)} & ${\runtotal}s \pm {\runtotalstd}s$ & ${\runfile}s \pm {\runfilestd}s$
  \end{tabular}
  \caption{Overview evaluation on essential constraints of the collected Spreadsheet dataset}
\end{table}
\samuel{Expand summary}
\sergey{would it make sense to specify the size of a spreadsheet in the number of non-zero cells?}
